---
title: "Course Project"
author: "Xinyi_Lin"
date: "10/18/2020"
output: html_document
---

## Input files

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(caret)
```

```{r}
pml.testing <- read.csv("./data/pml-testing.csv")
pml.training <- read.csv("./data/pml-training.csv")
```

```{r, eval=FALSE}
head(pml.testing)
head(pml.training)
summary(pml.testing)
summary(pml.training)
```

## Data cleaning

There are NA in the dataset. We should first clean those NA. First, we check the percentage of NA in some variables. We can find out variables either have high missing values or don't have missing values, so we can just keep those without missing values.

```{r}
NA_prc = colMeans(is.na(pml.training))
print(NA_prc)
rm_var = names(NA_prc[NA_prc>0.5])
training = pml.training %>% 
  select(-rm_var)
head(training)
```

When checking the training dataset, I found out there are some varibles are empty. Check the content and find out they are space. As these variables don't provide information, we should remove them.

```{r}
training$kurtosis_picth_belt[1]

rm_var2 = c("kurtosis_picth_belt", "kurtosis_yaw_belt", "skewness_roll_belt", "skewness_roll_belt.1", "skewness_yaw_belt", "max_yaw_belt", "min_yaw_belt", "amplitude_yaw_belt", "kurtosis_roll_arm", "kurtosis_picth_arm", "kurtosis_yaw_arm", "skewness_roll_arm", "skewness_pitch_arm", "skewness_yaw_arm", "kurtosis_roll_dumbbell", "kurtosis_picth_dumbbell", "kurtosis_yaw_dumbbell", "skewness_roll_dumbbell", "skewness_pitch_dumbbell", "skewness_yaw_dumbbell", "max_yaw_dumbbell", "min_yaw_dumbbell", "amplitude_yaw_dumbbell", "kurtosis_roll_forearm", "kurtosis_picth_forearm", "kurtosis_yaw_forearm", "skewness_roll_forearm", "skewness_pitch_forearm", "skewness_yaw_forearm", "max_yaw_forearm", "min_yaw_forearm", "amplitude_yaw_forearm")

training = pml.training %>% 
  select(-rm_var, -rm_var2)
```

## Variables Selection

As there are 61 variables left, we need to do variables selection to select variables used for final model building.

```{r}
x = model.matrix(classe~.,training)
y = training$classe
```

```{r}
set.seed(123)
ctrl1 = trainControl(method = "cv", number = 10)
lasso.fit = train(x,y, method = "glmnet", tuneGrid = expand.grid(alpha=seq(0.1, 1 ,length = 5), lambda = exp(seq(-1, 5, length = 20))), trControl = ctrl1)
plot(lasso.fit, xTrans = function(x)log(x))
saveRDS(lasso.fit, "./data/lasso_fit.rds")
```

